Supplement to Investigating the incidence and potential risk factors for hypertension-related mortalities in adults in the United States.

### 2025-05-05 products/manuscript/supplement/Supplement-CVD.qmd
updates for reproducibility and readmes

1. processing-code/processing-code.qmd 
2. eda-code/eda.qmd
3. analysis-code/statistical-analysis-v2-slim.qmd* 
4. products/manuscript/Manuscript.qmd
5. products/manuscript/supplement/Supplement-CVD.qmd

*Note: This is a large script and will take some time and processing power to run. The script uses loops to load saved data to reduce computation but expect it to take about 15 minutes to run the full script even with those steps.

@@

Note: processing-code/processing-code.qmd - This file will not run as the Excel CSV file is not in the repository due to size limitations. It was included purely to demonstrate processing steps. You can contact the author to get it or download the file directly from the CDC website if you wish to run this yourself.

### Software packages

@@

**Session packages:**\
*(includes attached and namespace-loaded packages)*

>>>>

1.  processing-code/processing-code.qmd^^ (Not required to reproduce results - This file will not run - see below)
2.  processing-code/processingfile-v1.qmd
3.  eda-code/eda.qmd
4.  analysis-code/statistical-analysis-v2-slim.qmd\*
5.  products/manuscript/Manuscript.qmd
6.  products/manuscript/supplement/Supplement-CVD.qmd

\*Note: This is a large script and will take some time and processing power to run. The script uses loops to load saved data to reduce computation but expect it to take about 15 minutes to run the full script even with those steps.

@@

^^Note: processing-code/processing-code.qmd - This file will not run as the Excel CSV file is not in the repository due to size limitations. It was included purely to demonstrate processing steps. You can contact the author to get it or download the file directly from the CDC website if you wish to run this yourself.

### Software Packages and Environment

All analyses presented in this project were performed using R within a version-controlled environment managed by the `renv` package. This ensures that all package versions and dependencies used to generate figures and tables are locked and reproducible.

To reproduce this analysis:

1.  Clone the repository.
2.  Open the project in R or RStudio.
3.  Restore the environment by running:

#renv::restore()

@@

**Key R Packages Used (Attached or namespace-loaded)**
